---
title: "Test3 overview"
author: "Pierre Ekelmans"
output:
  html_document:
    toc: no
    toc_float: yes
    theme: cerulean
  pdf_document:
    toc: no
  word_document:
    toc: no
---

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
source("LoadData.R")
```

# Introduction

Test 3 is another quick test which checks that the simulated network is in the expected state. This test also checks an input and a synapse classe (namely WhiteNoiseLinear, ExponentialSynapse).
This test simply consists in obseving that the simulated network is in a bistable regime.
```{r,include=FALSE}


project_name  = 'Test3';#project_name is an identifier of the folder containing the simulation data. It is the title of the simulation 
                        #The date suffix does not need to be included
base_path    = getwd();

folders_ = list.files(path = base_path,pattern=paste("*",project_name,"_20*",sep=""));
folder_name = paste(base_path,folders_[1],sep="/");
setwd(folder_name);
```


```{r,include=FALSE}
#Load main data file

number_populations <- Get_Number_of_Populations(folder_name);
data            <- Load_data(folder_name,number_populations);
```


## Result 

This plot shows the firing rate of the Excitatory population as a function of the external input. The system must be bistable, meaning that for the same input value (eg: 4mV/s), the system can be in two stable states: a high activity state and a low activity state.
The fact that the simulation shows this behaviour illustrates that the simulated network state matches the theoretical prediction.   

```{r,echo=FALSE}
#par(mfrow=c(3,1))
#par(mar=c(4,4,0,0))
csr0<- c(0,cumsum(data$r_0))
csr1<- c(0,cumsum(data$r_1))
n <- 10
mvr0<-(csr0[(n+1):length(csr0)] - csr0[1:(length(csr0)-n)])/n
mvr1<-(csr1[(n+1):length(csr1)] - csr1[1:(length(csr1)-n)])/n
plot(data$time*2/15-4/15*pmax(data$time-75, 0),data$r_0,type = "l",xlim = c(0,10),ylim=c(0,10),xlab = "External Input (mV/s)",ylab = "Firing Rate (Hz)")


```